The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-12-03 paper/paper.qmd
update paper

# Estimand

# Data {#sec-data}

## Overview
We employ the statistical programming language R [@citeR] to process, analyze, and visualize survey data that investigates how disruptions during interviews impact response quality. The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], which offers a rich collection of data on societal attitudes and behaviors across numerous European countries. The dataset includes multiple subsets tailored for different stages of analysis, allowing for a systematic examination of how various factors affect survey response quality. The primary dataset used for modeling comprises 9,743 rows and 25 variables, which capture essential details, including types of disruptions (such as partner, child, or other familial interference), methods of interview, and characteristics of respondents. The rigorous standardization of data collection across countries in the ESS ensures comparability and facilitates an in-depth inquiry of the impacts of contextual disruptions on response quality.

@@

Our analysis focuses on the following variables, with a specific focus on **respondent_understood_binary** as the dependent variable:

-   **respondent_understood_binary**: A binary variable indicating whether the respondent fully understood the survey questions. It was recoded as:

@@

-   **interview_conduct_method**: The method by which the interview was conducted, with the following possible categories:

@@

-   **child_interference**: Indicates whether interruptions by children occurred during the interview, with binary values:

@@

-   **partner_interference**: Indicates whether interruptions by partners occurred during the interview, with binary values:

@@

-   **question_clarification**: Tracks whether the respondent requested clarification on any survey questions. The variable includes:

@@

-   **respondent_reluctant**: Captures the level of reluctance exhibited by the respondent during the interview process. Possible levels include:

@@

-   **interviewer_age**: The age of the interviewer, used to explore whether interviewer demographics impact response quality.

-   **interviewer_gender**: The gender of the interviewer, categorized as:

@@

-   **Respondent Understanding (RESPONDENT_UNDERSTOOD_BINARY)**: Indicates whether the respondent fully comprehended the survey questions, categorized as *Understood* or *Not Understood*.
-   **Interview Conduct Method (INTERVIEW_CONDUCT_METHOD)**: Refers to the method of conducting the interview, including face-to-face interviews, telephone interviews, and self-administered surveys.
-   **Interference Factors**:
    -   **Child Interference (CHILD_INTERFERENCE)**: Documents whether interruptions occurred due to children during the interview (*Yes* or *No*).
    -   **Partner Interference (PARTNER_INTERFERENCE)**: Indicates whether the respondent’s partner interrupted the interview (*Yes* or *No*).
-   **Question Clarification (QUESTION_CLARIFICATION)**: Records whether the respondent asked for clarification on survey questions at any point.
-   **Respondent Reluctance (RESPONDENT_RELUCTANT)**: Reflects the respondent’s level of reluctance during the interview, categorized into levels from *Not Reluctant* to *Highly Reluctant*.
-   **Interviewer Age (INTERVIEWER_AGE)**: Specifies the age of the interviewer, which is included to examine possible influences of interviewer demographics.
-   **Interviewer Gender (INTERVIEWER_GENDER)**: Indicates the gender of the interviewer, recorded as *Male* or *Female*.

@@

-   $\beta_1$: The coefficient for **interview_conduct_method**, representing the type of interview conducted. This variable includes different categories such as:

@@

-   $\beta_2$: The coefficient for **partner_interference**, representing different levels of interference by the respondent's partner. Categories include:

@@

-   $\beta_3$: The coefficient for **child_interference**, indicating different levels of interference by children during the interview. This variable includes:

@@

-   $\beta_4$: The coefficient for **parent_interference**, indicating different levels of interference by the respondent's parents.

-   $\beta_5$: The coefficient for **relative_interference**, representing interference by other relatives.

-   $\beta_6$: The coefficient for **non_relative_interference**, indicating whether interference was caused by non-relatives.

-   $\beta_7$: The coefficient for **interviewer_age**, which is a continuous variable representing the age of the interviewer.

-   $\beta_8$: The coefficient for **interviewer_gender**, indicating the gender of the interviewer:

@@

-   $\beta_{10}$: The coefficient for **question_clarification**, indicating whether the respondent requested clarification during the interview. It includes multiple levels, such as:

@@

-   $\beta_{11}$: The coefficient for **respondent_reluctant**, representing the level of reluctance shown by the respondent. Categories include:

@@

-   $\beta_{12}$: The coefficient for **respondent_tried_best**, indicating whether the respondent tried their best to provide accurate answers during the survey. Categories include:

>>>>

# Data {#sec-data}
## Data Source
The dataset for this study is sourced from the [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], a widely recognized repository that provides detailed information on societal attitudes and behaviors across numerous European countries. The dataset includes various subsets designed for distinct stages of analysis, enabling an examination of how factors like disruptions influence survey responses. The primary dataset used for this research contains 9,743 rows and 25 variables, capturing details such as types of disruptions (e.g., partner or child interference), methods of interview, and characteristics of respondents. The standardized collection procedures employed by the ESS ensure consistency across countries, making the dataset well-suited for cross-national comparisons.

## Overview
We utilized the statistical programming language R [@citeR] to prepare, analyze, and visualize the survey data. This study focuses on understanding how interview disruptions affect response quality by examining variables related to both interviewer and respondent characteristics. The structured design of the dataset allowed for a thorough exploration of contextual disruptions and their influence on data reliability, providing valuable insights for enhancing survey methodologies.

@@

Our analysis focuses on the following variables, with a specific focus on **respondent understood binary** as the dependent variable:

-   **respondent understood binary**: A binary variable indicating whether the respondent fully understood the survey questions. It was recoded as:

@@

-   **interview conduct method**: The method by which the interview was conducted, with the following possible categories:

@@

-   **child interference**: Indicates whether interruptions by children occurred during the interview, with binary values:

@@

-   **partner interference**: Indicates whether interruptions by partners occurred during the interview, with binary values:

@@

-   **question clarification**: Tracks whether the respondent requested clarification on any survey questions. The variable includes:

@@

-   **respondent reluctant**: Captures the level of reluctance exhibited by the respondent during the interview process. Possible levels include:

@@

-   **interviewer age**: The age of the interviewer, used to explore whether interviewer demographics impact response quality.

-   **interviewer gender**: The gender of the interviewer, categorized as:

@@

-   **Respondent Understanding **: Indicates whether the respondent fully comprehended the survey questions, categorized as *Understood* or *Not Understood*.
-   **Interview Conduct Method**: Refers to the method of conducting the interview, including face-to-face interviews, telephone interviews, and self-administered surveys.
-   **Interference Factors**:
    -   **Child Interference**: Documents whether interruptions occurred due to children during the interview (*Yes* or *No*).
    -   **Partner Interference **: Indicates whether the respondent’s partner interrupted the interview (*Yes* or *No*).
-   **Question Clarification **: Records whether the respondent asked for clarification on survey questions at any point.
-   **Respondent Reluctance **: Reflects the respondent’s level of reluctance during the interview, categorized into levels from *Not Reluctant* to *Highly Reluctant*.
-   **Interviewer Age **: Specifies the age of the interviewer, which is included to examine possible influences of interviewer demographics.
-   **Interviewer Gender**: Indicates the gender of the interviewer, recorded as *Male* or *Female*.

@@

-   $\beta_1$: The coefficient for **interview conduct method**, representing the type of interview conducted. This variable includes different categories such as:

@@

-   $\beta_2$: The coefficient for **partner interference**, representing different levels of interference by the respondent's partner. Categories include:

@@

-   $\beta_3$: The coefficient for **child interference**, indicating different levels of interference by children during the interview. This variable includes:

@@

-   $\beta_4$: The coefficient for **parent interference**, indicating different levels of interference by the respondent's parents.

-   $\beta_5$: The coefficient for **relative interference**, representing interference by other relatives.

-   $\beta_6$: The coefficient for **non_relative interference**, indicating whether interference was caused by non-relatives.

-   $\beta_7$: The coefficient for **interviewer age**, which is a continuous variable representing the age of the interviewer.

-   $\beta_8$: The coefficient for **interviewer gender**, indicating the gender of the interviewer:

@@

-   $\beta_{10}$: The coefficient for **question clarification**, indicating whether the respondent requested clarification during the interview. It includes multiple levels, such as:

@@

-   $\beta_{11}$: The coefficient for **respondent reluctant**, representing the level of reluctance shown by the respondent. Categories include:

@@

-   $\beta_{12}$: The coefficient for **respondent tried_best**, indicating whether the respondent tried their best to provide accurate answers during the survey. Categories include:
